---
title: "Analysis"
editor: 
  markdown: 
    wrap: 72
---

Loading necessary libraries :

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggrepel)
library(reshape2)
library(gridExtra)
```

Load the data:

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

load("library_museum_updated.RData")
data <-library_museum_updated
```

For regional analysis, 'region' column will first be added to the data:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
akdeniz <- c("Antalya", "Burdur", "Isparta", "Mersin", "Adana", "Hatay", "Osmaniye", "Kahramanmaraş")
dogu_anadolu <- c("Malatya", "Erzincan", "Elazığ", "Tunceli", "Bingöl", "Erzurum", "Muş", "Bitlis", "Şırnak", "Kars", "Ağrı", "Ardahan", "Van", "Iğdır", "Hakkari")
ege <- c("İzmir", "Aydın", "Muğla", "Manisa", "Denizli", "Uşak", "Kütahya", "Afyonkarahisar")
guneydogu_anadolu <- c("Gaziantep", "Kilis", "Adıyaman", "Şanlıurfa", "Diyarbakır", "Mardin", "Batman", "Siirt")
ic_anadolu <- c("Eskişehir", "Konya", "Ankara", "Çankırı", "Aksaray", "Kırıkkale", "Kırşehir", "Yozgat", "Niğde", "Nevşehir", "Kayseri", "Karaman", "Sivas")
karadeniz <- c("Bolu", "Düzce", "Zonguldak", "Karabük", "Bartın", "Kastamonu", "Çorum", "Sinop", "Samsun", "Amasya", "Tokat", "Ordu", "Giresun", "Gümüşhane", "Trabzon", "Bayburt", "Rize", "Artvin")
marmara <- c("Çanakkale", "Balıkesir", "Edirne", "Tekirdağ", "Kırklareli", "İstanbul", "Bursa", "Yalova", "Kocaeli", "Bilecik", "Sakarya")

assign_region <- function(city) {
  if (city %in% akdeniz) {
    return("Akdeniz")
  } else if (city %in% dogu_anadolu) {
    return("Doğu Anadolu")
  } else if (city %in% ege) {
    return("Ege")
  } else if (city %in% guneydogu_anadolu) {
    return("Güneydoğu Anadolu")
  } else if (city %in% ic_anadolu) {
    return("İç Anadolu")
  } else if (city %in% karadeniz) {
    return("Karadeniz")
  } else if (city %in% marmara) {
    return("Marmara")
  } else {
    return(NA)
  }
}

data <- data %>% mutate(region = sapply(city, assign_region)) %>% relocate(region,.after = city)
data$region <- as.factor(data$region)
```

## 1) Correlation Between Attributes

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

correlation_matrix <- cor(library_museum_updated[, c(3:21)], use = "complete.obs")

melted_corr_matrix <- melt(correlation_matrix)

ggplot(melted_corr_matrix, aes(Var1, Var2, fill = value)) +
  geom_tile() + labs(x = " ", y = " ") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

In the areas where the squares are dark red, there is a positive
correlation between the variables. In cities with a high population, the
number of museums, libraries, theater and cinema audience numbers, and
the number of suicides are also high. Conversely, when the number of
pieces in a museum is high, it is observed that the number of museums,
libraries, audience numbers of theaters and cinemas are also high. The
variables intersecting in dark blue-purple squares, on the other hand,
have a negative correlation. That is, there is an inverse relationship
between the proportion of the young population and the literacy rate.

## 2) Relationship Between Attributes

### 2.1) Literacy Rate vs. Proportion of Youth Population

```{r}
#| code-fold: true
#| code-summary: "Show the code"
cor_pop_book_2 <- cor(data$literacy_rate, data$prop_youth_population)
cat("Correlation between Literacy Rate and Proportion of Youth Population:",cor_pop_book_2,"\n")
```

The correlation of - 0.69 indicates a negative relationship between
literacy rate and proportion of youth population. This situation may be
due to the number of children in the preschool age group.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data|>
  filter(year==2022)|>
ggplot(aes(x = literacy_rate, y = prop_youth_population, color = region)) +
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x)+ 
  labs(x = "Literacy Rate", y = "Proportion of Youth Population") + 
  ggtitle("Scatter Plot of Literacy Rate vs Proportion of Youth Population in 2022") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5))
```

This plot shows an inverse relationship between two attributes. Cities
in the Marmara region have a high literacy rate and a low youth
population, while the situation is the opposite for cities in the Doğu
Anadolu region. This may reflect the impact of socio-economic
differences between the Marmara and Doğu Anadolu regions, as well as the
effect of children entering the workforce at an early age.

### 2.2) Population vs. Number of Books

```{r}
#| code-fold: true
#| code-summary: "Show the code"
cor_pop_book <- cor(data$population, data$book_num)
cat("Correlation between Population and Number of Books:",cor_pop_book,"\n")
```

The correlation of 0.8455922 indicates a strong positive relationship
between population and the number of books. In other words, as the
population of cities generally increases, there is a tendency for the
number of books in libraries to increase as well. Let's try to support
this with visualizations.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data|>
  filter(year==2022) |>
ggplot( aes(x = population, y = book_num,color = region)) +
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x)+ 
  labs(x = "Population", y = "Book Count") + 
  ggtitle("Scatter Plot of Population vs Book Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5),axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_continuous(labels = scales::comma, breaks = seq(0, 15000000, by = 1000000))
```

According to the 2022 data from the Turkish Statistical Institute, 97.6%
of the cities in Turkey have a population of less than 5 million. As
seen in the above graph, the areas where the points are dense correspond
to locations with a population of less than 5 million. For this reason,
the following plot was created.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data %>%
  filter(population <= 5000000 & year==2022) %>%
  ggplot(aes(x = population, y = book_num,color = region)) +
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x) + 
  labs(x = "Population", y = "Book Count") + 
  ggtitle("Scatter Plot of Population vs Book Count (Max 5 Million Population)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_continuous(labels = scales::comma, breaks = seq(0, 5000000, by = 1000000))+ scale_y_continuous(labels = scales::comma)
```

We supported the correlation results with visualizations. We can say
that there is a tendency for the number of books in libraries to
increase as the population in cities generally increases.

### 2.3) City Comparison

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data %>%
  filter(year == 2022) %>%
  mutate(book_per_person=book_num/population,city = factor(city, levels = unique(city[order(book_per_person, decreasing = TRUE)]))) %>%
  ggplot(aes(x = city, y = book_per_person * 100)) +
  geom_point(color = "purple") +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x) + 
  labs(x = "Cities", y = "Book Number per Population (*100)") + 
  ggtitle("Scatter Plot of Cities vs Book Number per Population in 2022") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 90, hjust = 1, size = 6))
```

We looked into the number of books per capita in the population of each
city, as we believed it would provide a more meaningful insight in this
graph. The book count on the Y-axis was multiplied by 100. The graph is
based on data from the year 2022. According to the results,
surprisingly, Nevşehir and Bayburt appear to be leading cities in this
aspect. Cities with high populations and diverse demographics, such as
Istanbul, Ankara, Izmir, and Antalya, are at the bottom of the list. For
now, let's keep Bayburt in mind from this graph :)

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data %>%
  filter(year == 2022) %>%
  mutate(museum_per_person=((ministry_museum_num + private_museum_num)/population), city = factor(city, levels = unique(city[order(museum_per_person, decreasing = TRUE)]))) %>%
  ggplot(aes(x = city, y = museum_per_person * 100000)) +
  geom_point(color = "purple") +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x) + 
  labs(x = "Cities", y = "Museum Number per Population (*100000) ") + 
  ggtitle("Scatter Plot of Cities vs Museum Number per Population in 2022") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 90, hjust = 1, size = 6))

```

In this graph, you can see the ratio of the combined number of ministry
and private museums to the population of each city. The Y-axis has been
multiplied by 100,000 for meaningful representation, showing the number
of museums per 100,000 people.The graph is based on data from the year
2022. While Doğu and Güney Doğu cities are at the bottom of the list,
once again, Bayburt leads the chart.

```{r}
#| code-fold: true
#| code-summary: "Show the code"

data %>%
  filter(year == 2022) %>%
  mutate(book_num_per_lib=(book_num/public_lib), city = factor(city, levels = unique(city[order(book_num_per_lib, decreasing = TRUE)]))) %>%
  ggplot(aes(x = city, y = book_num_per_lib )) +
  geom_point(color = "purple") +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x) + 
  labs(x = "Cities", y = "Book Number per Library") + 
  ggtitle("Scatter Plot of Cities vs Book Number per Library in 2022") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 90, hjust=1,size=6))
```

At this point, we aimed to examine the ratio of library sizes among
cities by looking at the proportion of the number of books in a city to
the number of libraries. The graph is based on data from the year 2022.
The difference between Istanbul and Ankara is quite striking. There's
nearly a threefold difference in library sizes between Turkey's two most
populous cities. The leading city remains unchanged at the top position
in this aspect as well.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data %>%
  filter(year == 2022) %>%
  mutate(user_num_per_pop=(user_num/population), city = factor(city, levels = unique(city[order(user_num_per_pop, decreasing = TRUE)]))) %>%
  ggplot(aes(x = city, y = user_num_per_pop )) +
  geom_point(color = "purple") +  
  geom_smooth(method = "lm", se = FALSE, color = "yellow", formula = y ~ x) + 
  labs(x = "Cities", y = "User Number per Population") + 
  ggtitle("Scatter Plot of Cities vs User Number per Population in 2022") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 90, hjust=1,size=6))
```

It's time for Bayburt's leadership to change now, as we've reached the
statistics on library user counts :) The graph is based on data from the
year 2022. What's remarkable here is the higher user count-to-population
ratio is occured in smaller cities. In the top position, Batman stands
out, having a library usage statistic nearly three times its population.
We've considered the possibility of potential inaccuracies in the
records. Once again, our highly populated cities form the bottom of the
list. Another noteworthy point is Ankara's user count ratio being ahead
of Istanbul.

### 2.4) Library User Number and Population Change Over Time

To observe the change in library user number in the cities with the
highest population growth between 2015 and 2022, we start by identifying
the six cities where the population has changed the most.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| warning: false
population_2015 <- data %>%
  filter(year==2015) %>% select(city,population)
population_2022 <- data %>%
  filter(year==2022) %>% select(city,population)
population_change <- data %>%
  filter(year==2015) %>% select(city) %>% mutate(population_frac = (population_2022$population-population_2015$population)/population_2015$population) %>% arrange(desc(population_frac))

kable(head(population_change),
      caption = "Top 6 Cities in Turkey with the Highest Population Change",
      col.names = c("City", "Population Fraction"),
      align = c("c", "c")) 
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"

p1 <- data %>% 
  filter(city %in% c("Yalova","Tekirdağ","Antalya","Kocaeli")) %>% mutate(user_num_per_pop=(user_num/population)) %>%
  ggplot(aes(x = year, y = user_num_per_pop, color = city)) +
  geom_line() +  
  labs(x = "Years", y = "User Number per Population") + 
  ggtitle("Scatter Plot of Cities vs User Number per Population") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5)) + scale_x_continuous(breaks = seq(min(data$year), max(data$year), by = 1)) + theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 45, hjust=1,size=6))
p2 <- data %>% 
  filter(city %in% c("Yalova","Tekirdağ","Antalya","Kocaeli")) %>%
  ggplot(aes(x = year, y = population/10000000, color = city)) +
  geom_line() +  
  labs(x = "Years", y = "Population/10M") + 
  ggtitle("Scatter Plot of Cities vs Population") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5)) + scale_x_continuous(breaks = seq(min(data$year), max(data$year), by = 1)) + theme(plot.title = element_text(size = 12, hjust = 0.5), axis.text.x = element_text(angle = 45, hjust=1,size=6))

grid.arrange(p1, p2, ncol = 2)
```

In the graph, we can observe that the city with the highest population
growth, Yalova, experienced a significant increase in library user
numbers between 2015 and 2019. However, in Antalya, despite substantial
population growth, there is not a significant increase in library users.
Between 2019 and 2021, there is a noticeable decline in library user
numbers, influenced by the impact of the pandemic. As of 2022, these
numbers seem to be on the rise again.

## 3) Regional Analysis

### 3.1) Cinema-Theater Audience Numbers

```{r}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true
data %>%
  filter(year %in% c(2022,2015)) %>%
  pivot_longer(cols = c(cinema_audiences_num, theater_audiences_num), names_to = "Audience_Type", values_to = "Audience_Num") %>%
  ggplot(aes(x = region, y = Audience_Num, fill = Audience_Type)) +
  geom_boxplot(position = "dodge") +
  scale_y_log10() +
  labs(x = "Region", y = "Audience Number (log10)", fill = "Audience Type") +
  ggtitle("Cinema and Theater Audience Numbers by Region") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + scale_fill_manual(values = c("Red", "Blue"), labels = c("Cinema", "Theater"), name = "Audience Type") +
  facet_grid(.~year)

```

In the graph, we can see the distributions of the number of theater and
cinema audiences in each region represented on a box plot. In all
regions, cinema audiences are higher than theater audiences.
Additionally, looking at the years 2015 and 2022, it is observed that
there hasn't been much change in these audience numbers.

### 3.2) Ministry and Private Museum Visitors

```{r}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true
data %>%
  filter(year %in% c(2022,2015)) %>%
  pivot_longer(cols = c(ministry_museum_visitor_num, private_museum_visitor_num), names_to = "Visitor_Type", values_to = "Visitor_Num") %>%
  ggplot(aes(x = region, y = Visitor_Num, fill = Visitor_Type)) +
  geom_boxplot(position = "dodge") +
  scale_y_log10() +
  labs(x = "Region", y = "Visitor Number (log10)", fill = "Museum Type") +
  ggtitle("Ministry and Private Museum Visitor Numbers by Region") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + facet_grid(.~year) + scale_fill_manual(values = c("Pink", "Purple"), labels = c("Ministry Museum", "Private Museum"), name = "Museum Type")
  
```

In the graph, the number of visitors of both ministry and private
museums in each region is shown with box plot distributions. In the
Akdeniz and Ege regions, the difference in visits to these two types of
museums is more pronounced compared to other regions. Excluding the
Karadeniz and Marmara regions, there has been an increase in visitor
numbers to ministry museums in all regions over the years. Istanbul has
the highest number of ministry museum visitors, while Düzce, excluding
those with zero visitors, has the lowest number of private museum
visitors.

### 3.3) Museum Visitor and Loaned Book

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"

data$total_museum_visitor_num <- data$ministry_museum_visitor_num+ data$private_museum_visitor_num
data %>%
  filter(year==2020) %>%
  pivot_longer(cols = c(total_museum_visitor_num,loaned_book_num), names_to = "Variable_Type",  values_to = "Value") %>%
  ggplot(aes(x = region, y = Value, fill = Variable_Type)) +
  geom_boxplot(position = "dodge") +
  scale_y_log10() +
  labs(x = "Region", y = "Value (log10 scale)", fill = "Variable Type") +
  ggtitle("Visitor Numbers and Loaned Book Rates by Region") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + 
  facet_grid(.~year) + 
  scale_fill_manual(values = c("darkgreen", "orange"), 
                    labels = c("Total Museum Visitor", "Loaned Book Rate"), 
                    name = "Variable Type")


```

-HATİCE AÇIKLAMA-

## 4) Rate Distributions

### 4.1) Rate Distributions across Years

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"


data$`Library User Rate` <- data$user_num / data$population
data$`Borrowed Book Rate` <- data$loaned_book_num / data$user_num
data$`Suicide Rate` <- data$suicides_num * 10000 / data$population
data$`Cinema Audience Rate` <- data$cinema_audiences_num / data$population
data$`Theater Audience Rate` <- data$theater_audiences_num / data$population


rate_of_data <- data %>%
  select(city, year, `Library User Rate`, `Borrowed Book Rate`, 
         `Suicide Rate`, `Cinema Audience Rate`, `Theater Audience Rate`)


tidy_data <- rate_of_data %>%
  pivot_longer(
    cols = c(`Library User Rate`, `Borrowed Book Rate`, 
             `Suicide Rate`, `Cinema Audience Rate`, `Theater Audience Rate`),
    names_to = "rate_type",
    values_to = "rate_value"
  )


ggplot(tidy_data, aes(x = year, y = rate_value, fill = rate_type)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  labs(
    title = "Rate Distributions across Years",
    x = "Years",
    y = " Value",
    fill = " Types"
  ) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
  scale_fill_brewer(palette = "Set2")


```

-HATİCE AÇIKLAMA-

### 4.2) Rate Distributions for Regions

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"


data$`Library User Rate` <- data$user_num / data$population
data$`Borrowed Book Rate` <- data$loaned_book_num / data$user_num
data$`Suicide Rate` <- data$suicides_num * 10000 / data$population
data$`Cinema Audience Rate` <- data$cinema_audiences_num / data$population
data$`Theater Audience Rate` <- data$theater_audiences_num / data$population


rate_of_data <- data %>%
  select(region, year, `Library User Rate`, `Borrowed Book Rate`, 
         `Suicide Rate`, `Cinema Audience Rate`, `Theater Audience Rate`)


tidy_data <- rate_of_data %>%
  filter(year == 2020) %>%
  pivot_longer(
    cols = c(`Library User Rate`, `Borrowed Book Rate`, 
             `Suicide Rate`, `Cinema Audience Rate`, `Theater Audience Rate`),
    names_to = "rate_type",
    values_to = "rate_value"
  )


ggplot(tidy_data, aes(x = region, y = rate_value, fill = rate_type)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  labs(
    title = "Rate Distributions for Regions",
    x = "Region",
    y = " Value",
    fill = " Types"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set2")




```

-HATİCE AÇIKLAMA-

## 5) Top 10 Comparison

### 5.1) Cinema Audience Number of Top 10 Cities

```{r}
#| code-fold: true
#| code-summary: "Show the code"
top_cities_2020 <- data %>%
  filter(year == 2020) %>%
  arrange(desc(cinema_audiences_num)) %>%
  slice(1:10)


ggplot(top_cities_2020, aes(x = population, y = cinema_audiences_num, label = city, color = city)) +
  geom_point() +
  geom_text_repel(size = 3.5) +
  theme_minimal() +
  labs(title = "Cinema Audience Distribution by Population in 2020",
       x = "Population",
       y = "Cinema Audiences Number") +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(labels = scales::comma)

correlation <- cor(top_cities_2020$population, top_cities_2020$cinema_audiences_num, use = "complete.obs")
cat("Correlation between population and cinema audiences number:",correlation,"\n")
```

The chart shows the distribution between the population of the provinces
in Turkey and the number of people going to the cinema. The correlation
coefficient of 0.9982, which is a very high value, indicates a strong
linear relationship between population and cinema attendance numbers.
Therefore, as we can see from the table and correlation value, as the
population increases, the number of people going to the cinema increases
almost at the same rate.

### 5.2) The Effect of Literacy Rate on Suicide Rates of Top 10 Cities

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data_2020 <- data %>%
  filter(year == 2020)

top_literacy_cities_2020 <- data_2020 %>%
  arrange(desc(literacy_rate)) %>%
  slice_head(n = 10)

ggplot(top_literacy_cities_2020, aes(x = loaned_book_num, y = suicides_num, color = city)) +
  geom_point() +
  geom_text_repel(aes(label = city)) +
  labs(x = "Loaned Book Number", y = "Number of Suicides",
       title = "The Effect of Literacy Rate on Suicide Rates in 2020") +
  theme_minimal() +
  theme(legend.position = "right")

correlation <- cor(top_literacy_cities_2020$loaned_book_num, top_literacy_cities_2020$suicides_num, use = "complete.obs")
cat("Correlation between loaned book number and number of suicides:",correlation,"\n")
```

This chart shows the relationship between the number of books borrowed
from libraries and suicide rates. Ankara appears to have the highest
number of book borrowings and suicides; Izmir also has similarly high
values. The given correlation coefficient is 0.9717, which is a very
high and positive value. In other words, it may suggest that as the
number of books borrowed increases, the number of suicides also
increases.

## 6) The Number of Historical Remnants in Cities

```{r}
#| code-fold: true
#| code-summary: "Show the code"
top5_ruins <- data %>%
  filter(year == 2022) %>%
  arrange(desc(ruins_num)) %>%
  head(5) %>%
  select(city, ruins_num)
kable(top5_ruins, 
      format = "html", 
      caption = "Top 5 Cities in Turkey with the Highest Number of Historical Remnants in 2022",
      col.names = c("City", "Historical Remnants"),
      align = c("c", "c")) 
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
data %>%
  filter(year == 2022 & ruins_num > 0) %>%
  mutate(city = factor(city, levels = unique(city[order(ruins_num, decreasing = FALSE)]))) %>%
  arrange(desc(ruins_num)) %>%
  ggplot(aes(x = city, y = ruins_num)) +
  geom_bar(stat = "identity", fill = "purple", color = "yellow") +
  labs(x = "City", y = "Number of Historical Remnants") +
  ggtitle("The number of historical remnants in cities in Turkiye (2022)") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 0, hjust = 1, size = 5),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size = 12, hjust = 0.5)) +
  scale_x_discrete(breaks = unique(data$city)) +
  scale_y_continuous(breaks = seq(0, max(data$ruins_num), by = 1))+
  coord_flip()

```
